Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
One more spacing fix

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic Diagram for our symmetric lens synthesis algorithm. Regular
    expressions \Regex and \RegexAlt, and a set of examples \Examples, are
    provided as input. \Expand searches through stochastic regular expression
    pairs, equivalent to the originals, and proposes them to \GreedySynth.
    \GreedySynth finds a lens, typed between the generated equivalent pairs.
    When the algorithm determines it has an optimal lens, it returns that lens.}
  \label{fig:high-level-algorithm}
\end{figure}

@@

  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{vlightyellow}}c|>{\columncolor{vlightgreen}}c|}
      \hline
      \texttt{company.mgmt} data file & \texttt{company.hr} data file \\
      \hline
      \listingA & \listingB \\
      \hline
      \cellcolor{lightyellow}\texttt{company.mgmt} regular expression & 
      \cellcolor{lightgreen}\texttt{company.hr}  regular expression\\
      \hline
      \cellcolor{lightyellow}\listingC & \cellcolor{lightgreen}\listingD \\
      \hline
    \end{tabular}
  }
  \caption{Hypothetical example data files and corresponding regular expressions
  used by management and HR at a US company to represent employee salaries and health
  insurance providers, respectively. \ksf{Why
  is \lstinline{emp_salaries} written with an or instead of just using
  the star operator? Can we simplify?}\afm{It does require the or operator, if
  we don't want it to have trailing or preceding newlines.  Howevever, I
  intentionally had this as not having those to force a discussion about
  rewrites and searching through rewrites.} }  
  \label{fig:minimized-representations}
\end{figure}

@@

\[
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \ConcatLensOf{\Lens_1}{\Lens_2} \OfType \BRegex_1 \Concat \BRegex_2
    \Leftrightarrow
    \BRegexAlt_1 \Concat \BRegexAlt_2
  }
\]
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1 \String_2$ & = & $(\Lens_1.\CreateROf{\String_1})(\Lens_2.\CreateROf{\String_2})$\\
%    $\CreateL{} \App \StringAlt_1 \StringAlt_2$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
%    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_1\StringAlt_2)$ & = & $(\Lens_1.\PutROf{\String_1}{\StringAlt_1})(\Lens_2.\PutROf{\String_2}{\StringAlt_2})$\\
%    $\PutL{} \App (\StringAlt_1\StringAlt_2) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
%  \end{tabular}
%\end{center}

Concat is similar to concatenation in existing string lens languages like
Boomerang.  For such terms, we do not provide the semantics, and merely refer
readers to existing work.

\[
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \SwapLensOf{\Lens_1}{\Lens_2} \OfType \BRegex_1 \Concat \BRegex_2
    \Leftrightarrow
    \BRegexAlt_2 \Concat \BRegexAlt_1
  }
\]
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\String_2$ & = & $(\Lens_2.\CreateROf{\String_2})(\Lens_1.\CreateROf{\String_1})$\\
%    $\CreateL{} \App \StringAlt_2\StringAlt_1$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
%    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_2\StringAlt_1)$ & = & $(\Lens_2.\PutROf{\String_2}{\StringAlt_2})(\Lens_1.\PutROf{\String_1}{\StringAlt_1})$\\
%    $\PutL{} \App (\StringAlt_2\StringAlt_1) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
%  \end{tabular}
%\end{center}
The swap combinator is similar to concat, though the second regular expression
is swapped.

\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \OrLensOf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \RegexOr{\BRegexAlt_1}{\BRegexAlt_2}
  }
  $
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

>>>>

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic diagram for our symmetric lens synthesis algorithm. Regular
    expressions \Regex and \RegexAlt, and a set of examples \Examples, are
    provided as input. \Expand searches through stochastic regular expression
    pairs, equivalent to the originals, and proposes them to \GreedySynth.
    \GreedySynth finds a lens, typed between the generated equivalent pairs.
    When the algorithm determines it has an optimal lens, it returns
  that lens. \ksf{Figure needs to be changed to call first search
  Expand; Are the S and T regular expressions (which should have bars)
  or stochastic regular expressions (which should be called such)?}}
  \label{fig:high-level-algorithm}
\end{figure}

@@

  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{vlightyellow}}c|>{\columncolor{vlightgreen}}c|}
      \hline
      \texttt{company.mgmt} data file & \texttt{company.hr} data file \\
      \hline
      \listingA & \listingB \\
      \hline
      \cellcolor{lightyellow}\texttt{company.mgmt} regular expression & 
      \cellcolor{lightgreen}\texttt{company.hr}  regular expression\\
      \hline
      \cellcolor{lightyellow}\listingC & \cellcolor{lightgreen}\listingD \\
      \hline
    \end{tabular}
  }
  \caption{Hypothetical example data files and corresponding regular expressions
  used by management and HR at a US company to represent employee salaries and health
  insurance providers, respectively. }  
  \label{fig:minimized-representations}
\end{figure}

@@

\begin{centermath}
\begin{tabular}[b]{l@{\qquad \; \qquad}l}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \ConcatLensOf{\Lens_1}{\Lens_2} \OfType \BRegex_1 \Concat \BRegex_2
    \Leftrightarrow
    \BRegexAlt_1 \Concat \BRegexAlt_2
  }
$
&
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \SwapLensOf{\Lens_1}{\Lens_2} \OfType \BRegex_1 \Concat \BRegex_2
    \Leftrightarrow
    \BRegexAlt_2 \Concat \BRegexAlt_1
  }
$
\end{tabular}
\end{centermath}
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1 \String_2$ & = & $(\Lens_1.\CreateROf{\String_1})(\Lens_2.\CreateROf{\String_2})$\\
%    $\CreateL{} \App \StringAlt_1 \StringAlt_2$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
%    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_1\StringAlt_2)$ & = & $(\Lens_1.\PutROf{\String_1}{\StringAlt_1})(\Lens_2.\PutROf{\String_2}{\StringAlt_2})$\\
%    $\PutL{} \App (\StringAlt_1\StringAlt_2) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
%  \end{tabular}
%\end{center}

Concat is similar to concatenation in existing string lens languages like
Boomerang.  For such terms, we do not provide the semantics, and merely refer readers to existing work. The swap combinator is similar to concat, though the second regular expression
is swapped.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\String_2$ & = & $(\Lens_2.\CreateROf{\String_2})(\Lens_1.\CreateROf{\String_1})$\\
%    $\CreateL{} \App \StringAlt_2\StringAlt_1$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
%    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_2\StringAlt_1)$ & = & $(\Lens_2.\PutROf{\String_2}{\StringAlt_2})(\Lens_1.\PutROf{\String_1}{\StringAlt_1})$\\
%    $\PutL{} \App (\StringAlt_2\StringAlt_1) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
%  \end{tabular}
%\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \OrLensOf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \RegexOr{\BRegexAlt_1}{\BRegexAlt_2}
  }
  $
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\
